{\sc Kalashnikov}: Fully Automatic Loop Free Program Synthesis by Bounded Model Checking

### 2013-10-04 paper/paper.tex
Changes to paper

\usepackage{listings}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows, automata, shapes}

@@

\section{Related Work}

@@

\label{fig:synth-dfd}
\caption{Schematic diagram of {\sc verif}}
\end{figure}

@@

@@

>>>>

\usepackage{listings}
\usepackage{graphicx}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows, automata, shapes}

@@

\section{Related Work}
The most similar work to ours is {\sc brahma}~\cite{brahma}, which is also a method for
synthesizing loop-free bitvector programs.  Specifications for the

@@

\label{fig:verif-dfd}
\caption{Schematic diagram of {\sc verif}}
\end{figure}

@@

\begin{figure}
 \begin{lstlisting}[language=c]
s  = a + b;
b2 = s - a;
a2 = s - b2;
db = b - b2;
da = a - a2;
t  = da + db;
 \end{lstlisting}

\begin{lstlisting}[language=c]
s = a + b;
z = s - a;
t = b - z;
\end{lstlisting}

 \label{fig:2sum}
 \caption{2Sum}
\end{figure}

@@

We performed our experiments on a 4-core, 3.07GHz Xeon X5667 with 50GB of RAM.

\begin{figure}
 \includegraphics[width=\linewidth]{figures/brahma_kalashnikov.pdf}
 \label{fig:brahma-kalashnikov}
 \caption{Brahma runtimes vs. Kalashnikov}
\end{figure}
